Work Stress

### 2023-03-15 outputs/paper/paper.qmd
commit before pull

Work is the most common cause of many people to get stress. Work stress can be found in many forms for people. In this paper, we will examine job status, work hours, industry sector, satisfaction rate of your job into the correlation of work stress levels. There are many analysis to talk about relevant to work stress.

In this paper, we gathered data from (Publisher Name), (Data Name). With the gathered data, we generated figures to observe the trend in work stress of different categories using R [@citeR]. We also uploaded and cleaned data using R [@citeR], tidyr [@citetidyr], dplyr [@citedplyr], tidyverse [@citetidyverse], and haven [@citehaven] packages. Figures and tables were created with knitr [@citeknit], ggplot2 [@citeggplot], kableExtra [@citekable], and dplyr [@citedplyr].

In section 2 we discuss the source of the data used in this paper, the strengths and weaknesses the source and methodology contains, and potential blind spots that the data misses. Section 3 discusses the results that is being produced from the figure and what it tells us by its visualization. Section 4, we would provide a brief discussion about what we get from all figures, and make some thoughts. In section 5 there is an optional survey used to gather more information about stress caused by job status, work hours, industry sector, satisfaction rate of your job into the correlation of work stress levels.

@@

```{r setup}
#| echo: false
#| message: false
#| label: fig-1
#| fig-cap: Work Stress by Job Status
#Load libraries
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(wrkstat, stress) %>% 
  filter(str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"),
         str_detect(wrkstat, "Working full time|Working part time"))

@@

```{r}
#| echo: false
#| message: false
#| label: fig-2
#| fig-cap: Work Stress by Work Hours
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(hrs1, stress) %>% 
  filter(!str_detect(hrs1, ".i|.y|.n|.d"), str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"))

@@

```{r}
#| echo: false
#| label: fig-3
#| fig-cap: Work Stress by Industry Sector
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(wrkgovt, stress) %>% 
  filter(str_detect(wrkgovt, "Government|Private"),
         str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"))

@@

```{r}
#| echo: false
#| label: fig-4
#| fig-cap: Work Stress by Job Satisfaction
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(satjob, stress) %>% 
  filter(str_detect(satjob, "Very satisfied|Moderately satisfied|A little dissatisfied|Very dissatisfied"),
         str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"))

@@

## Work Stress Levels

Even though work stress have different causes. We believe that the major cause or initial step into work stress would traffic delays. There are always traffic delays that most commuters would face almost every day. Most of these commuters are people going for work especially during rush hour time. Satisfaction rate is very important for jobs, and most people are sometimes not satisfy, its mainly due to these traffic delays. For example, if you are taking Greater Toronto Area commuters, most jobs are found in downtown Toronto, North York, and Mississauga. The GTA is going far west as Hamilton to east as Durham Region. Most of these commuters will be spending at least 1 hour of commuting to their workplace either by car or public transit. In an anonymized therapy session in 2014, a client expressed: “by the the time I get home from work, I’m just, you know, after that drive, I’m just so dead, it’s like, you know, shaking and don’t want to drive anymore. I don’t want to do anything else. . . sometimes I like if there’s been lots of traffic or like if I’ve been tired and like been forcing myself to stay awake so I can get home.” Traffic is the main issue that we believe that is is impacting the job satisfaction rate, which is why lots of people are facing work stress. We need to find a solution that can reduce the traffic, increase job satisfaction, and if possible these can expect to reduce the work stress for everyone.

## Work Hours of a Work Shift & Weekly Schedule

Right now most professionalists are working 40 hours a week, 8 hours shift each day. There is a plan of increasing work hours to 10 hours shift, and work only 4 days each week. But, based on some data, it is definitely not recommended to increase work hours because currently lots of people are always facing work stress when the number of hours are higher. So, if the work shift gets extended longer to reduce the total number of work days, this may cause more work stress because lots of people will be stress over number of tasks to complete during work. Other alternatives that can be used to reduce work stress can be reducing the total number of hours per week from 40 hours to 35 hours. This will allow people to face less work stess because it will reduce the number of hours for them working, and we believe 7 hours work shift can be enough to complete important tasks in a job.

>>>>

To measure birth rates, the National Center for Health Statistics (NCHS) aggregates data on birth rates for women by age, race, education level, and other factors; the aggregated data for a particular year is the total number of births per 1000 women. Each year NCHS measures birth rates nationwide and analyzes the data to make insights into societal phenomena. For instance, in 1997, NCHS published a paper on how a mother's education level influences the birth rate. In the paper, NCHS asserted that there is a negative correlation between a mother's education level and birth rate. Their study found a direct relationship between years of education and birth rates, with the highest birth rates among women with the lowest educational attainment @citeNCHS.

In this paper, we gathered data from the American Economic Association, National Center for Health Statistics, and the U.S. population data. With the gathered data, we generated graphs and tables to observe the trend in birth rates of different demographics using R [@citeR]. We also uploaded and cleaned data using R [@citeR], tidyr [@citetidyr], dplyr [@citedplyr], tidyverse [@citetidyverse], and haven [@citehaven] packages. Figures and tables were created with knitr [@citeknit], ggplot2 [@citeggplot], kableExtra [@citekable], and dplyr [@citedplyr].

@fig-1 depicts U.S. birth rate trends over the last 40 years. Here, we can see that the trend is fluctuating relatively stable. However, during the post-2007 recession, it takes a steep decline with no sign of returning. We start our journey to explore potential explanations for the decline.

In @sec-first-point, we discuss how decomposing the decline in the birth rate between demographic groups offers us a clearer picture of the topic. As shown in @fig-2, by dissecting the demographics into age groups and ethnicity groups, we notice a significant decrease among the white ethnicity women between ages 15 and 24, while other ethnic groups are showing a minor decrease.

@sec-second-point, briefly discusses the empirical relationship between birth rates and economics and policy factors. We then argue that other economic, policy or social factors that have changed since 2007 do not contribute much to the decline.

@sec-third-point, presents a potential attributing factor for the declining U.S. birth rate after the 2007 recession. We show strong evidence that suggests the most recent group of young adults is a significant driver of the post-2007 decline in the birth rate. This significance suggests that the societal shifts among young women moving through childbearing age are an ongoing trend.

We conclude the paper by raising a concern that this societal phenomenon imposes some severe societal consequences and, therefore, should be considered at a high level. Most importantly, we need to consider what it means for the nation's well-being when there are no signs of returning from the negative trend in birth rates.

@@

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| label: fig-1
#| fig-cap: Work Stress by Job Status
#Load libraries
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(wrkstat, stress) %>% 
  filter(str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"),
         str_detect(wrkstat, "Working full time|Working part time"))

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-2
#| fig-cap: Work Stress by Work Hours
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(hrs1, stress) %>% 
  filter(!str_detect(hrs1, ".i|.y|.n|.d"), str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"))

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-3
#| fig-cap: Work Stress by Industry Sector
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(wrkgovt, stress) %>% 
  filter(str_detect(wrkgovt, "Government|Private"),
         str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"))

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-4
#| fig-cap: Work Stress by Job Satisfaction
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(satjob, stress) %>% 
  filter(str_detect(satjob, "Very satisfied|Moderately satisfied|A little dissatisfied|Very dissatisfied"),
         str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"))

@@

## Birth Rates by Demographic Groups {#sec-first-point}

In 1997, NCHS released a report titled "Mother's Educational Level Influences Birth Rate." According to the report, a women's education level is the best predictor of how many children she will have. In the report, NCHS describes a direct relationship between years of education and birth rates, with the highest birth rates among women with the lowest educational attainment [@citeNCHS].\
We are particularly interested in ethnic groups of ages 15-19 and 20-24. @fig-2 shows a sharp decline in birth rates among all groups of women between the age of 15 to 19 during the post-2007 recession. @fig-2 also shows a sharp decline over the same period; however, only among white ethnic women between the ages 20 to 24, while other groups show a relatively steady decline. Figures that are omitted from this paper of the other age groups (25 to 34 and 35 to 44) show a similar trend both in pre and post-recession. However, as shown in @tbl-1, the most significant contributor to the decline in the birth rate is Hispanic, with less than High School education, women between ages 20-24 after 2007. This result contradicts the earlier claim made by NCHS. The finding suggests, in the post-2007 recession, the women's education level and birth rate now correlate positively.

## Economic and Policy Factors {#sec-second-point}

In @fig-4, we show other economic factors that might have negatively affected the birth rate in the post-2007 recession across the states. Although the graphs show their inverse relationship, no dramatic change is shown. For instance, as there were somewhere around \$1000 to \$2000 increases in childcare expenses over the past 13 years, we see that the decrease in the actual birth rate is only between 0 to -10. Change in per capita student loans also has increased between \$2500 to \$3250, but it only contributed to the decrease somewhere between 0 to -5 across the states. Based on these findings, it is hard to find an explanation of the dramatic decline in the birth rate since 2007 from economic factors.
